\documentclass[]{kyvernitis-resume}
\fullname{Zhongtao Guan}
% \jobtitle{Sofware Engineer}

\begin{document}
\resumeheader
{\email{guanzht@shanghaitech.edu.cn}}
{\github{Coming Soon}}
{\phone{+86 18321822460}}
{\website{Coming Soon!}}
{\nationality{CHINA}}

\begin{section}{Education}
    \begin{subsectionnobullet}{Shanghaitech University}{Shanghai, China}{Sep. 2021 -- Present}{}
        \item{Bachelor of Engineering,Electrical engineering}
       \item{Overall GPA-\textbf{3.80/4.0}, Major Rank-\textbf{2/55}, Overall Rank-\textbf{8/230}}
    \end{subsectionnobullet}
\end{section}

\begin{section}{Publication}
    \begin{enumerate}
        \item \textbf{Zhongtao Guan}, Jun Wan, Yu Liu, Dian Lu, Mengzhao Duan and Renke Huang. Accurate Single-Ended Fault Location for Cable-OHL Hybrid Transmission Lines. Power and Energy Society General Meeting (PESGM), 2023. %\textbf{h5:82}
        \item Jiayu Yang, Yu Liu*, Kang Yue, \textbf{Zhongtao Guan}, Minfan Fu and Haoyu Wang, “Closed-Form Solutions of Mutual Inductance and Load for LCC-S Wireless Power Transfer Systems”, in 3rd IEEE International Conference on Industrial Electronics for Sustainable Energy Systems, Jul. 2023.
        \item Mengzhao Duan, Yu Liu, Ze Liu, Xinchen Zou and \textbf{Zhongtao Guan}. “A Group of Single-Ended Time-Domain Line Fault Location Methods Using Breaker Operation Information”, in IEEE Power and Energy Society General Meeting (PESGM), 2023.%\textbf{h5:82}
    \end{enumerate}
\end{section}

\begin{section}{Research Experience}
\begin{subsection}{\textbf{\href{https://pspal.shanghaitech.edu.cn/}{Power System Protection \& Automation Laboratory}}}{Mentors: Prof. Liu Yu}{ 6.2022 -- 8.2023}{ShanghaiTech University}
    \item{Using single-ended measurement to locate faults on the mixed-transmission line.}
    \item{Design a low-Cost inverter with brand-new devices for plugging renewable energy into smart grid.}
\end{subsection}
\begin{subsection}{ \textbf{\href{https://faculty.sist.shanghaitech.edu.cn/chenjh/}{Motor and Motion-Control Lab }}}{Mentors: Prof. Chen Jiahao}{ 8.2023--Present}{ShanghaiTech University}
    \item{Mechanical Design and Control of biped robot.}
    \item{Design actuators for biped robot.}
\end{subsection}
\end{section}


\begin{section}{Projects and Competition}
    \begin{subsection}{\textbf{Robomaster}}{Robot Competition}{9.2021-6.2022}{}
        \item{Lead and coordinate a group for experimental robot design and development.}
         \item{Responsible for mechanical design and routine maintenance.}

    \end{subsection}
    \begin{subsection}{\textbf{Inverter Design and Control}}
    {Individual Project}{Spring 2023}{}
\item{Realize Phase-loop and close-loop control algorithms on Ti's C2000 micro controller.}
\item{Design related PCB Using Altium Designer.}
    \end{subsection}
        \begin{subsection}{\textbf{Bandit Algorithm}}
    {Group Project}{Autumn 2022}{}
\item{Realize and compare the performance of $\epsilon$-greedy , UCB(upper confidence bound) and TS(Thompson Sampling) algorithms.}
\item{ Design more practical cases and adjust algorithms to obtain better performance.}
\end{subsection}
\end{section}

\newpage

\begin{section}{Work and Volunteer Experience}
 \begin{subsection}{\textbf{Introduction to Electric Circuit}}
    {Teaching Assistant}{Spring 2023}{ShanghaiTech University}
\item{Responsible to course recording, tutorial classes; set questions and answers.}
    \end{subsection}
\begin{subsection}{\textbf{Volunteer Teaching in Yunnan}}
    {Volunteer Teacher}{Spring 2022}{ShanghaiTech University}
\item{Teaching Physics and Chinese for children in one of Dali's depressed village.}
\item{Continue donate salary of teaching assistant through United Nations Children's Fund.}
    \end{subsection}
\end{section}

\sectiontable{Awards}{
    \entry{Excellent Student}{\textbf{Top 3\%} \hfill \textit{2022}}
    \entry{Outstanding Individual in Social Practice}{ \hfill \textit{2022}}
    \entry{ RoboMaster University Championship (Eastern Division)}{ 2nd Prize\hfill \textit{2022}}
    \entry{ RoboMaster University Championship (National)}{ 3rd Prize\hfill \textit{2022}}
    \entry{Outstanding Teaching assistant}{ \hfill \textit{2023}}
    \entry{National Undergraduate Electronic Design Contest(Shanghai Division)}{2nd Prize\hfill \textit{2023}}
}
\begin{section}{Skills and Courses}
\item{Programming Skills and Software: C/C++, python, MATLAB, Simulink, Code Composer Studio, Altuim Designer, Solidworks}
\end{section}
\end{document}
