\documentclass[]{ZhongtaoGuan-resume}
\fullname{Zhongtao Guan}
% \jobtitle{Sofware Engineer}

\begin{document}
\resumeheader
{\email{guanzht@shanghaitech.edu.cn}}
{\github{DoZz-M}}
{\phone{+86 18321822460}}
{\website{DoZz-M.github.io}}
{\nationality{CHINA}}

\begin{section}{Education}
 \begin{subsectionnobullet}{Shanghaitech University}{Shanghai, China}{09. 2021 - Present}{}
     \item {School of Information Science and Technology}
     \item{Bachelor of Engineering, Electronic Information Engineering}
     \item{Overall GPA: \textbf{3.81/4.0}, Major rank: \textbf{2/55}, Overall rank: \textbf{8/230}}
 \end{subsectionnobullet}
\end{section}

\begin{section}{Publication}
 \begin{enumerate}
     \item \textbf{Zhongtao Guan}, Jun Wan, Yu Liu*, Dian Lu, Mengzhao Duan and Renke Huang. “Accurate Single-Ended Fault Location for Cable-OHL Hybrid Transmission Lines”, in Power and Energy Society General Meeting (PESGM), Orlando, Florida, USA, 2023. %\textbf{h5:82}
     \item Jiayu Yang, Yu Liu*, Kang Yue, \textbf{Zhongtao Guan}, Minfan Fu and Haoyu Wang, “Closed-Form Solutions of Mutual Inductance and Load for LCC-S Wireless Power Transfer Systems”, in the 3rd IEEE International Conference on Industrial Electronics for Sustainable Energy Systems, Jul. 2023.
     \item Mengzhao Duan, Yu Liu*, Ze Liu, Xinchen Zou and \textbf{Zhongtao Guan}. “A Group of Single-Ended Time-Domain Line Fault Location Methods Using Breaker Operation Information”, in IEEE Power and Energy Society General Meeting (PESGM), 2023.%\textbf{h5:82}
    \end{enumerate}
\end{section}

\begin{section}{Research Experience}
 \begin{subsection}{\textbf{\href{https://pspal.shanghaitech.edu.cn/}{Power System Protection \& Automation Laboratory}}}{Adviors: Prof. Yu Liu}{ 6.2022 -- 8.2023}{ShanghaiTech University}
     \item{Develop a single-ended measurement to locate faults on the mixed-transmission line.}
     \item{Design a low-cost inverter with new types of devices for plugging renewable energy.}
 \end{subsection}
 
 \begin{subsection}{ \textbf{\href{https://faculty.sist.shanghaitech.edu.cn/chenjh/}{Motor and Motion-Control Lab }}}{Adviors: Prof. Jiahao Chen}{ 8.2023 -- Present}{ShanghaiTech University}
     \item{Mechanical design and control for quasi-direct-drive bipedal robot.}\hfill{\textbf{Ongoing}}
     \item{Nonlinear B-controller: design and optimization for dynamical gain controller.}\hfill{\textbf{Ongoing}}
 \end{subsection}
\end{section}


\begin{section}{Selected Projects and Competitions} 
 \begin{subsection}{\textbf{Robomaster}}{Robot Competition}{9.2021-6.2022}{}
     \item{Lead and coordinate a group for experimental robot design and development.}
     \item{Responsible for mechanical design and routine maintenance.}

 \end{subsection}
 \begin{subsection}{\textbf{National Undergraduate Electronic Design Contest (Shanghai Division)}}
     {Individual Project}{Summer 2023}{}
     \item{Realize single-phase-loop and close-loop control algorithms on STM32 microcontroller.}
     \item{Design related PCB use Altium Designer.}
 \end{subsection}
 \begin{subsection}{\textbf{Bandit Algorithm}}
     {Group Project}{Autumn 2022}{}
     \item{Realize and compare the performance of $\epsilon$-greedy, UCB (upper confidence bound) and TS (Thompson Sampling) algorithms.}
     \item{Design more practical cases and adjust algorithms to reach better performance.}
 \end{subsection}
\end{section}

\newpage

\begin{section}{Work and Volunteer Experience}
 \begin{subsection}{\textbf{Electric Circuit}}
     {Head Teaching Assistant}{Spring 2023}{ShanghaiTech University}
     \item{Responsible to course recording, tutorial classes; set homeworks and corresponding answers.}
     \item {Collaborated with Professor Yu Liu on grading and exam supervision.}
     \item{2023 SIST Outstanding Teaching Assistant.}
 \end{subsection}
 \begin{subsection}{\textbf{Volunteer Teaching in Yunnan}}
     {Volunteer Teacher}{Spring 2022}{ShanghaiTech University}
     \item{Teaching Physics and Chinese for children in one of Dali's depressed village.}
     \item{Continue donating salary of teaching assistant through United Nations Children's Fund.}
 \end{subsection}
\end{section}

\sectiontable{Awards}{
    \entry{Outstanding Student}{Top 3\% \hfill \textit{2022}}
    \entry{Outstanding Individual in Social Practice}{ \hfill \textit{2022}}
    \entry{RoboMaster University Championship (Eastern Division)}{ 2nd Prize\hfill \textit{2022}}
    \entry{RoboMaster University Championship (National)}{ the 3rd Prize\hfill \textit{2022}}
    \entry{Outstanding Teaching Assistant}{ \hfill \textit{2023}}
    \entry{National Undergraduate Electronic Design Contest (Shanghai Division)}{2nd Prize\hfill \textit{2023}}
    \entry{Outstanding Student}{Top 1-2\% \hfill \textit{2023}}
    \entry{Outstanding Individual in Industrial Practice}{ \hfill \textit{2023}}
}
\begin{section}{Courses and Skills}

\begin{subsectionnobullet}{\textbf{Coursework:}}{}{}{}
 \item {Introduction to Power Electronics, Probability and Statistics, Numerical Optimization, Introduction to Control, Introduction to Programming,
Signals and Systems, Electric Circuit (as TA), Digtial/Analog Circuit, Power System, Modern Woodworking Design and Practice}
\end{subsectionnobullet}
\begin{subsectionnobullet}{\textbf{Programming}}{}{}{}
    \item {C/C++, Python, MATLAB, AMPL, Pygmo, Numpy, Scipy, Pandas}
\end{subsectionnobullet}
\begin{subsectionnobullet}{\textbf{Software}}{}{}{}
    \item {Altium Designer, SolidWorks, KiCad, CCS}
\end{subsectionnobullet}
\begin{subsectionnobullet}{\textbf{Languages}}{}{}{}
    \item {Chinese (Native), English (Fluent)}
\end{subsectionnobullet}
\end{section}
\end{document}