\documentclass[]{ZhongtaoGuan_CV}
\fullname{Zhongtao Guan}
% \jobtitle{Sofware Engineer}

\begin{document}
\resumeheader
{\email{zhtguan@mit.edu}}
{\github{https://github.com/DoZz-M}}
{\phone{+1 6177846900}}
{\website{DoZz-M.github.io}}
{\nationality{CHINA}}

\begin{section}{Education}
 \begin{subsectionnobullet}{Shanghaitech University}{Shanghai, China}{Sep. 2021 - Present}{}
     \item{Bachelor of Engineering, Electronic Information engineering}
     \item{Overall GPA-\textbf{3.80/4.0}, Major Rank-\textbf{2/55}, Overall Rank-\textbf{8/230}}
 \end{subsectionnobullet}
 
 \begin{subsectionnobullet}{Massachusetts Institute of Technology}{Massachusetts, U.S.}{Feb. 2024 - May.2024}{}
     \item {Special Student Program}
     \item {Overall GPA-\textbf{5.0/5.0}}
 \end{subsectionnobullet}
\end{section}


\begin{section}{Publication}
 \begin{enumerate}
     \item \textbf{Zhongtao Guan}, et al. “Accurate Single-Ended Fault Location for Cable-OHL Hybrid Transmission Lines”, in Power and Energy Society General Meeting (PESGM), 2023. %\textbf{h5:82}
     \item Jiayu Yang, Yu Liu*, Kang Yue, \textbf{Zhongtao Guan}, Minfan Fu and Haoyu Wang, “Closed-Form Solutions of Mutual Inductance and Load for LCC-S Wireless Power Transfer Systems”, in 3rd IEEE International Conference on Industrial Electronics for Sustainable Energy Systems, Jul. 2023.
     \item Mengzhao Duan, Yu Liu*, Ze Liu, Xinchen Zou and \textbf{Zhongtao Guan}. 'A Group of Single-Ended Time-Domain Line Fault Location Methods Using Breaker Operation Information', in IEEE Power and Energy Society General Meeting (PESGM), 2023.%\textbf{h5:82}
     \item \textbf{Zhongtao Guan}, et al. "Cury: A Backdrivable Leg Design using Linear Actuators ", International Conference on Intelligent Robots and Systems (IROS 2024), Under review.
 \end{enumerate}
\end{section}

\begin{section}{Research Experience}
\begin{subsection}{ \textbf{\href{https://smrl.mit.edu/}{SOFT AND MICRO ROBOTICS LABORATORY }}}{Undergraduate Visiting Student Mentors: Prof. Kevin Chen}{ Jun.2024--Present }{Massachusetts Institute of Technology}
     \item{Sensor autonomy of insect-scale robots.}
 \end{subsection}
\begin{subsection}{ \textbf{\href{https://smrl.mit.edu/}{SOFT AND MICRO ROBOTICS LABORATORY }}}{UROP at MIT, Mentors: Prof. Kevin Chen}{ Jan.2024--May.2024 }{Massachusetts Institute of Technology}
     \item{Trajectory optimization and MPC tracking for a insect-scale hopping flapping wing robots.}
 \end{subsection}
 
\begin{subsection}{ \textbf{\href{https://faculty.sist.shanghaitech.edu.cn/chenjh/}{Motor and Motion-Control Lab }}}{Research Assistant, Mentors: Prof. Chen Jiahao}{ Aug.2023--Jan.2024 }{ShanghaiTech University}
     \item{Mechanical design and control of bipedal robot.}
     \item{ Actuators design for bipedal robot for backdrivable and energy recovery.}
     \item{Design of four-in-one motor drivers.}
     \item {Using parameter curve for controller design.}
 \end{subsection}
 \begin{subsection}{\textbf{\href{https://pspal.shanghaitech.edu.cn/}{Power System Protection \& Automation Laboratory}}}{Research Assistant, Mentors: Prof. Liu Yu}{ Jun..2022 -- Aug..2023}{ShanghaiTech University}
     \item{Fault Location of the mixed-transmission line using single-ended measurements.}
     \item{Low-Cost inverter design for  renewable energy .}
 \end{subsection}
 
\end{section}

\newpage

\begin{section}{Projects and Competition}
 \begin{subsection}{\textbf{Robomaster}}{Robot Competition}{9.2021-6.2022}{}
     \item{Lead and coordinate a group for experimental robot design and development.}
     \item{Responsible for mechanical design and routine maintenance.}

 \end{subsection}

 \begin{subsection}{\textbf{Bandit Algorithm}}
     {Group Project}{Autumn 2022}{}
     \item{Realize and compare the performance of $\epsilon$-greedy , UCB(upper confidence bound) and TS(Thompson Sampling) algorithms.}
     \item{ Design more practical cases and adjust algorithms to obtain better performance.}
 \end{subsection}
\end{section}

% \newpage

\begin{section}{Work and Volunteer Experience}
 \begin{subsection}{\textbf{Electric Circuit}}
     {Teaching Assistant}{Spring 2023}{ShanghaiTech University}
     \item{Responsible to course recordings, tutorial classes; Problem sets and answers.}
 \end{subsection}
 \begin{subsection}{\textbf{Volunteer Teaching in Yunnan}}
     {Volunteer Teacher}{Spring 2022}{ShanghaiTech University}
     \item{Teaching Physics and Chinese for children in one of Dali's depressed village.}
     \item{Continue donating salary of teaching assistant through United Nations Children's Fund.}
 \end{subsection}
\end{section}

\sectiontable{Awards}{
    \entry{Excellent Student}{\textbf{Top 1-3\%} \hfill \textit{2022}}
    \entry{Outstanding Individual in Social Practice}{ \hfill \textit{2022}}
    \entry{ RoboMaster University Championship (Eastern Division)}{ 2nd Prize\hfill \textit{2022}}
    \entry{ RoboMaster University Championship (National)}{ 3rd Prize\hfill \textit{2022}}
    \entry{Outstanding Teaching assistant}{ \hfill \textit{2023}}
    \entry{National Undergraduate Electronic Design Contest (Shanghai Division)}{2nd Prize\hfill \textit{2023}}
    \entry{Excellent Student}{\textbf{Top 1- 3\%} \hfill \textit{2023}}
}
\sectiontable{Skills }{
\entry{Programming}{ C/C++, Python, MATLAB, Julia, \LaTeX}
\entry{Software}{Simulink, Altuim Designer, Kicad, Solidworks, Code Composer Studio}
\entry{Framework}{Numpy, Git, Anaconda, FORCEPRO, SNOPT, AMPL}
\entry{Platform}{Vicon Motion Capture System, Crazy File}
}

\end{document}
